### 2012-12-05 inst/examples/policycosts/writeup.Rmd
added fishstock plots to example

``` {r  parallel}
require(snowfall)
sfInit(cpu=8, parallel=T)
sfLibrary(pdgControl)
sfExportAll()
````

@@

```{r helperfn1}
fig4 <- function(fraction_lost){
closest <- function(x, v){
  which.min(abs(v-x))
}
dt_npv <- data.table(fees)
index <- dt_npv[,closest(fraction_lost, (npv0-value)/npv0), by=variable]
apples_index <- index$V1
names(apples_index) = index$variable
apples <- c2[index$V1]
names(apples) = index$variable
L2_policy <- policies$L2[[apples_index["L2"]]]$D
L1_policy <- policies$L1[[apples_index["L1"]]]$D
fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
free_increase_policy <- policies$free_increase[[apples_index["free_increase"]]]$D
free_decrease_policy <- policies$free_decrease[[apples_index["free_decrease"]]]$D
quad_policy <- policies$quad[[apples_index["quad"]]]$D

@@

```{r} 
# Helper functions to extract the summary stats in different variables
stats_harvest <- function(dt){
v <- dt[,var(harvest), by=c("penalty_fn", "reps")]
acor <- dt[,acf(harvest, plot=F)$acf[2], by=c("penalty_fn", "reps")]
df <- cbind(v, acor$V1)
setnames(df, c("V1", "V2"), c("var", "acor")) # names are nice
df
}

@@

```{r helper2}
#' a simple function for reorganizing the data over the different "faction-lost" levels
get_trends <- function(tmp2){
  out <- melt(tmp2, id=c("reps", "var", "acor"))
  colnames(out) = c("reps", "var", "acor", "nothing", "penalty", "index")
  out <- cbind(out[c(1,2,3,5)], fraction = frac_lost[out$index])
  out <- data.table(out)
  Ev = out[,mean(var),by=c('penalty', 'fraction')]
  SDv = out[,sd(var),by=c('penalty', 'fraction')]
  Ea = out[,mean(acor),by=c('penalty', 'fraction')]
  SDa = out[,sd(acor),by=c('penalty', 'fraction')]
  harvest_trends <- data.table(penalty = Ev$penalty, 
                               fraction = Ev$fraction, 
                               Ev = Ev$V1, Ea = Ea$V1, 
                               SDv=SDv$V1, SDa = SDa$V1)
}
```

```{r Figure4}
frac_lost <- seq(0,1, length=20)
sims_at_each_apple <- lapply(frac_lost, fig4)
harvest_stats <- lapply(sims_at_each_apple, stats_harvest)
havest_trends <- get_trends(harvest_stats)

Fig4a <- ggplot(harvest_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")

@@

```{r}
fishstock_stats <- lapply(sims_at_each_apple, stats_fishstock)
fishstock_trends <- get_trends(fishstock_stats)

>>>>

``` {r  parallel}
require(snowfall)
sfInit(cpu=2, parallel=T)
sfLibrary(pdgControl)
sfExportAll()
````

@@

```{r}
frac_lost <- seq(0,1, length=20)
```

```{r helper_fn_1}
fig4 <- function(fraction_lost){
closest <- function(x, v){
  which.min(abs(v-x))
}
dt_npv <- data.table(fees)
index <- dt_npv[,closest(fraction_lost, (npv0-value)/npv0), by=variable]
apples_index <- index$V1
names(apples_index) = index$variable
apples <- c2[index$V1]
names(apples) = index$variable

L2_policy <- policies$L2[[apples_index["L2"]]]$D
L1_policy <- policies$L1[[apples_index["L1"]]]$D
fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
free_increase_policy <- policies$free_increase[[apples_index["free_increase"]]]$D
free_decrease_policy <- policies$free_decrease[[apples_index["free_decrease"]]]$D
quad_policy <- policies$quad[[apples_index["quad"]]]$D

@@

```{r helper_fn_2} 
# Helper functions to extract the summary stats in different variables
stats_harvest <- function(dt){
v <- dt[,var(harvest), by=c("penalty_fn", "reps")]
acor <- dt[,acf(harvest, plot=F)$acf[2], by=c("penalty_fn", "reps")]
df <- cbind(v, acor$V1)
setnames(df, c("V1", "V2"), c("var", "acor")) # names are nice
df
}

@@

```{r helper_fn_3}
#' a simple function for reorganizing the data over the different "faction-lost" levels
get_trends <- function(tmp2){
  out <- melt(tmp2, id=c("reps", "var", "acor"))
  colnames(out) = c("reps", "var", "acor", "nothing", "penalty", "index")
  out <- cbind(out[c(1,2,3,5)], fraction = frac_lost[out$index])
  out <- data.table(out)
  Ev = out[,mean(var),by=c('penalty', 'fraction')]
  SDv = out[,sd(var),by=c('penalty', 'fraction')]
  Ea = out[,mean(acor),by=c('penalty', 'fraction')]
  SDa = out[,sd(acor),by=c('penalty', 'fraction')]
  harvest_trends <- data.table(penalty = Ev$penalty, 
                               fraction = Ev$fraction, 
                               Ev = Ev$V1, Ea = Ea$V1, 
                               SDv=SDv$V1, SDa = SDa$V1)
}
```

```{r Figure4_harvest}
sims_at_each_apple <- lapply(frac_lost, fig4)
harvest_stats <- lapply(sims_at_each_apple, stats_harvest)
harvest_trends <- get_trends(harvest_stats)
```

```{r Figure4}
Fig4a <- ggplot(harvest_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")

@@

```{r Figure4S}
fishstock_stats <- lapply(sims_at_each_apple, stats_fishstock)
fishstock_trends <- get_trends(fishstock_stats)
